Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2022-04-27 article/draft.tex
cosmetic changes

\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
\author{Dana Almanla, Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
\date{September 27, 2021}
\maketitle

@@

Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references). While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation. The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}

@@

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see Appendix \ref{links} for references).

@@

More specifically, we survey in this article a number of common policies against misinformation used by Facebook, Twitter and YouTube. We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$ 
informing users with flags and notices, and $(iii)$ reducing the visibility of some content. We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article. Furthermore, the examples provided to illustrate how to monitor a given policy were picked out of a list of domain names with several failed fact-checks. To be more precise, some domain names with failed fact-checks were picked because a given platform communicated about an intervention or because an intervention (e.g. suspension) was announced on the social media accounts linked to a given domain name. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.

@@

The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Iffy.news and feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/S4}{https://open.feedback.org/media/S4}.}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint. We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

Finally, suspending a Twitter account is an intervention which aims at penalizing users, in order to make them respect the Twitter rules. In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media published articles on the website. Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the 
articles published on lifesitenews.com were still being actively shared by other Twitter users.

@@

In this section, we turn to the suspension policy of YouTube. 
When a YouTube channel publishes a video that violates the community guidelines for the first time, it will usually receive a warning. 
But for the second violation, the channel receives its first strike.
A strike means that users are not allowed to post content on their YouTube channel for one week.
A strike remains associated to a channel for 90 days, and if a second strike occurs in same 90-day period as the first strike, the suspension will then last for two weeks.
A third strike results in the termination of the channel.\footnote{https://support.google.com/youtube/answer/2802032}
To illustrate the implementation of this policy, we use the following YouTube channels as two examples of  one-week suspensions: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

@@

The website of One America News Network has a ``low'' factual reporting score according to iffy.news and several inaccurate articles according to feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}  
According to NBC news (2020)~\cite{nbcnews}, the YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
We collected the number of video uploaded and the number of view of this channel using the YouTube API v3, between November $2020$ and January $2021$. For the video counts, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view counts on June $2021$.
%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

Tony Heller writes regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to iffy.news.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
Tony Heller tweeted on September 29, 2020 about his YouTube channel being `shut down' because of a video about an anti-covid-lockdown doctor getting arrested (see the right panel of Figure \ref{tweets_about_yt_suspensions}).
We applied the same methods as in the previous example to collect data.
Again a one-week suspension period from September $29$ until October $5$ can be observed clearly in the daily number of uploaded videos and of views (see Figure \ref{delete_youtube_tony}).
Comparing one month before and after the suspension, this channel also witnessed a drop of view counts by $-70\%$.

@@

As most YouTube channels upload videos on a weekly or even a monthly basis, a one-week suspension appears not very restrictive at first sight. 
But we observed that the intervention was followed by a reduction in the number of view for the two channels investigated, with one channel even stopping its YouTube activity in the following months. 
Although more research is needed before drawing a definitive conclusion, it is possible that the one-week suspension following a strike might reduce the reach of the very active YouTube channels.

@@

To the best of our knowledge, two types of flags can currently be displayed on Facebook posts: 
$(i)$ information banners which do not refute the message in the post and provide a link which redirects to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and $(ii)$ fact-check flags that assigns a ``rating" for a text or a link in a given post, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}). The fact-check flags display the following ratings : ``False", ``Partly false", ``Missing context", ``False headline", ``Altered media", ``Opinion", ``Satire", ``Not eligible" and ``True".\footnote{See \href{https://www.facebook.com/business/help/341102040382165}{https://www.facebook.com/business/help/341102040382165}.}

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/} \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{3835629366473816} .} 
\label{fb_flags}
\end{figure}

No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data. The only way to verify Facebook’s flagging policy is thus via scraping publicly available content. To that end, we added a new feature in Minet~\cite{minet} which could automatically verify the presence or absence of flags.

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

@@

In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to indicate content which is inaccurate or false. To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. 
As a second step, we collected (on June $30$, $2021$) using Minet~\cite{minet} all the tweets that have shared a link which belongs to the set of $3$ $094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets. To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}. Among those $657$ tweets only $3$ contained the label {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
	%\end{multicols}
	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial. Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel. Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing false or inaccurate information. 
We collected the information panels, when present, under each video by scraping the content of the web page. 
Three types of information panels were found regarding COVID-19, COVID-19 Vaccine, and climate change, as shown in figure \ref{youtube_panel_screenshots}.

@@

To illustrate, we investigate the case of the website $Infowars$. This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}. Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the Media Bias / Fact Check resource of Iffy.news and it has several failed fact-checks reported by Feedback.org.\footnote{See the Iffy.news page \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/} and Feedback.org \href{https://open.feedback.org/media/RM}{https://open.feedback.org/media/RM}.}

@@

Another measure that platforms can apply is to prevent users from sharing specific types of content, like URLs belonging to a specific domain name.  
The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.
\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} 
Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook''.
\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}

@@

The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban. We can note that although the ban was communicated in an article published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$. The communication around the ban appeared to have discouraged The Beauty of Life to proceed with their activity. Indeed the number of articles they published daily was around $50$ until December $20$, $2019$, when it decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).

@@

As we collected the recommendations of misinformation videos, we expected to find a high proportion of videos of questionable content.
But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation.
However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
It appears that the recommendation system of YouTube is reducing the visibility of certain videos but not of unauthoritative channels.

>>>>

\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
\date{September 27, 2021}
\maketitle

@@

Furthermore, mainstream platforms are increasingly engaging in editorial-like tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references). While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation. The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies point towards the idea that misinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}

@@

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The misinformation phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society when it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see Appendix \ref{links} for references).

@@

More specifically, in this article, we survey a number of common policies against misinformation used by Facebook, Twitter and YouTube. We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$ 
informing users with flags and notices, and $(iii)$ reducing the visibility of some content. We compile in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article. Furthermore, the examples provided to illustrate how to monitor a given policy were picked out of a list of domain names with several failed fact-checks. To be more precise, some domain names with failed fact-checks were picked because a given platform communicated about an intervention or because an intervention (e.g. suspension) was announced on the social media accounts linked to a given domain name. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.

@@

The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Media Bias Fact Check and open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/S4}{https://open.feedback.org/media/S4}.}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint. We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

@@

Finally, suspending a Twitter account is an intervention which aims at penalizing users, in order to make them respect the Twitter rules. In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media articles published on their website. Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the 
articles published on lifesitenews.com were still being actively shared by other Twitter users.

@@

In this section, we turn to the suspension policy of YouTube. 
When a YouTube channel publishes a video that violates the community guidelines for the first time, it will usually receive a warning. 
But for the second violation, the channel receives its first strike.
A strike means that users are not allowed to post content on their YouTube channel for one week.
A strike remains associated to a channel for 90 days, and if a second strike occurs in the same 90-day period as the first strike, the suspension will then last for two weeks.
A third strike results in the termination of the channel.\footnote{https://support.google.com/youtube/answer/2802032}
To illustrate the implementation of this policy, we use the following YouTube channels as two examples of  one-week suspensions: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

@@

The website of One America News Network has a ``low'' factual reporting score according to the website Media Bias Fact Check and several inaccurate articles according to open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}  
According to NBC news (2020)~\cite{nbcnews}, the YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
We collected the number of video uploaded and the number of view of this channel using the YouTube API v3, between November $2020$ and January $2021$. For the video counts, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view counts on June $2021$.
%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

Tony Heller writes regularly blog posts on the website {\it realclimatescience.com}, which also has a ``low'' factual reporting score according to the website Media Bias Fact Check.\footnote{See \href{https://mediabiasfactcheck.com/real-climate-science/}{mediabiasfactcheck.com/real-climate-science/}}
Tony Heller tweeted on September 29, 2020 about his YouTube channel being `shut down' because of a video about an anti-covid-lockdown doctor getting arrested (see the right panel of Figure \ref{tweets_about_yt_suspensions}).
We applied the same methods as in the previous example to collect data.
Again a one-week suspension period from September $29$ until October $5$ can be observed clearly in the daily number of uploaded videos and of views (see Figure \ref{delete_youtube_tony}).
Comparing one month before and after the suspension, this channel also witnessed a drop of view counts by $-70\%$.

@@

As most YouTube channels upload videos on a weekly or even a monthly basis, a one-week suspension does not appear very restrictive at first sight. 
But we observed that the intervention was followed by a reduction in the number of view for the two channels investigated, with one channel even stopping its YouTube activity in the following months. 
Although more research is needed before drawing a definitive conclusion, it is possible that the one-week suspension following a strike might reduce the reach of the very active YouTube channels.

@@

To the best of our knowledge, two types of flags can currently be displayed on Facebook posts: 
$(i)$ information banners which do not refute the message in the post and provide a link which redirects to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and $(ii)$ fact-check flags that assigns a ``rating" for a text or a link in a given post, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}). The fact-check flags can display one of the following ratings : ``False", ``Partly false", ``Missing context", ``False headline", ``Altered media", ``Opinion", ``Satire", ``Not eligible" and ``True".\footnote{See \href{https://www.facebook.com/business/help/341102040382165}{https://www.facebook.com/business/help/341102040382165}.}

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021.} 
\label{fb_flags}
\end{figure}
%\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/} \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{3835629366473816} .} 
No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data. The only way to verify Facebook’s flagging policy is thus via scraping publicly available content. To that end, we added a new feature in Minet~\cite{minet} which could automatically verify the presence or absence of flags.

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet without an information notice. Right Panel: Tweet containing an information notice.}
	\label{fig8}
\end{figure}

%	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}

@@

In this section, we take a deeper look at how labels and interstitials are introduced by Twitter, to add context to potentially inaccurate or misleading content. To that end, we gathered a set of $3$ $094$ links redirecting to articles which were marked as ``False'' between April $2019$ and February $2021$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. 
As a second step, we collected (on June $30$, $2021$) using Minet~\cite{minet} all the tweets that have shared a link which belongs to the set of $3$ $094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { \it ``Get the facts about COVID-19''}, $5$ tweets contained the label {\it ``Learn about US 2020 election security efforts''} and only $1$ had the following label {\it ``This claim about election fraud is disputed''}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same link, among the set of collected tweets. To give an example, $657$ tweets had shared the exact same link redirecting to a video on Bitchute, entitled {\it Important information on coronavirus 5G Kung Flu}. Among those $657$ tweets only $3$ contained the label {\it ``Get the facts about COVID-19''} (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by other users.

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
	%\end{multicols}
	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial. Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}
%	\caption{Left Panel: Tweet containing a URL link hidden behind an interstitial. Right Panel: when clicking on $view$, to view the content hidden behind the interstitial in the left panel. Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
\smallskip

@@

To further study the assignment of information panels to videos, we compiled a list of $170$ YouTube videos, fact-checked by Science Feedback between April $2019$ and March $2021$ and marked as containing inaccurate information. 
We collected the information panels, when present, under each video by scraping the content of the web page. 
Three types of information panels were found regarding COVID-19, COVID-19 Vaccine, and climate change, as shown in figure \ref{youtube_panel_screenshots}.

@@

To illustrate, we investigate the case of the website $Infowars$. This website appears in the Misinformation Directory of FactCheck.org, among other websites who have posted deceptive content\footnote{See \href{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}{https://www.factcheck.org/2017/07/websites-post-fake-satirical-stories/}.}. Furthermore, the factual reporting of $Infowars$ has been rated {\it very low} by the website Media Bias Fact Check and it has several failed fact-checks reported by open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/infowars-alex-jones/}{https://mediabiasfactcheck.com/infowars-alex-jones/} and open.feedback.org \href{https://open.feedback.org/media/B9}{https://open.feedback.org/media/B9}.}

@@

Another measure that platforms can apply is to prevent users from sharing specific types of content, like URLs belonging to a specific domain name.  
The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company operated by The Epoch Times that shares pro-Trump views and conspiracy theories such as QAnon.
\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} 
Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook''.
\footnote{\url{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}}

@@

The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban. We note that although the ban was communicated in an article published on December $20$, $2019$, it seems to have actually started on December $1$, $2019$. The communication around the ban appeared to have discouraged The Beauty of Life to proceed with their activity. Indeed the number of articles they published daily was around $50$ until December $20$, $2019$, when it decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel).

@@

As we collected the recommendations of misinformation videos, we expected to find a high proportion of videos of questionable content.
But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation.
However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended.
It appears that the recommendation system of YouTube is reducing the visibility of certain videos but not of unreliable channels.
